A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-14 manuscript/reply_to_reviewers.tex

	Overall, we hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course). 
	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort. That is emphatically not the case (we find the idea absurd), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty. We hope that it is now clear that the Bayesian framework we promote is a complement to high sampling effort.

	Once again, we thank the Associate Editor and Reviewers for their comments and hope that our revised manuscript will satisfy their concerns.

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	The Reviewer complimented our manuscript as ``well-written'' and addressing the ``hugely important'' question prior choice in network analyses. He/she supports our suggestion that researchers use their system-specific knowledge when embarking upon Bayesian analyses, and has suggested that we restructure the manuscript (especially the introduction) in order to come more directly to the issue of prior choice. In the present revision we have taken this advice to heart and streamlined our introduction in order to expand our discussion of prior choice. In this revision, we have retained some of the introductory material which the Reviewer notes describes ``ground very well-trod'' in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand. We hope that the introduction now strikes a balance between providing essential background information for Bayesian novices and moving quickly enough for those who do not need such a gentle introduction. We thank the Reviewer for their feedback and address each point (prefaced by \textbf{R:}) below.

@@

	1. Suggestion to refocus on prior selection

		\begin{refquote}
			In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. ... Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion. 
			\end{refquote}

		\textbf{R:} We thank the Reviewer for his/her positive evaluation, and have done our utmost to reframe and tighten the introduction and framing of the paper. In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes. Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 253). We also touch upon the controversy over using empirical priors (lines 348-353) although we were unable to find many references addressing this in detail. We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.

		In implementing the Reviewer's comments on our introduction, we believe that most readers who are less familiar with Bayesian procedures will need a quick outline of the problem of uncertain detection of interactions in order to be motivated to dive into the larger discussion of priors. We stress that our intended target audience is empirical ecologists working on network description who likely have a different skillset than that of the Reviewer. We also note that Reviewer 2 found that \emph{``The introduction is particularly pleasant to read and the problem is well stated"}, praise which we would hate to loose. Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection. We have, however, taken care to introduce our analysis as a worked example (lines 355) and hope that this helps to reduce the conflict between the introduction and our data.

@@

		Overall, we thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach. Thus, we have refined the introduction to be more specific about the problem we are attempting to solve. We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.

	2. Suggestion to add more literature

		\begin{refquote}
		The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations. We have incorporated these references as suggested (including Jordano, 2016 in the sampling section). Following comments from other reviewers, we have refined and restructured our introduction in the hope of more clearly establishing the goal of our manuscript. We hope that this revised introduction will also meet with the Reviewer's approval.

### 2019-01-14 manuscript/CI_interactions.tex
main text is now within word-count limits

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 6 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6872 % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).

@@

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L_{ij} = 1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij} = 1) = \chi_{ij}$. It is unlikely that $\chi_{ij} = 1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij} < 1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

@@

        \subsubsection*{Did we observe all interactions that occurred?}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L_{ij} = 1$ and $X_{ij} = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D_{ij}|X_{ij} = 1,L_{ij} = 1)=\delta_{ij}$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.

          Some types of interactions will have higher detection uncertainty than others. Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species. Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

    \subsection*{Can't we just sample more?}

        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}. Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.

        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions. We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites. This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites). The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}. For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system. This is straightforward to do using a Bayesian approach, as detailed below.

@@

    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda_{ij}$ is:

    %     \begin{equation}
    %       \lambda_{MLE} = \frac{k}{n}  .
    %       \label{theta_MLE}
    %     \end{equation}

    % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij} = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

@@

    % All of the above methods for estimating the variance of $\lambda_{ij}$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

>>>>

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6871 % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is critical to understanding species' effects on each other and predicting the community's response to perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework for combining observed data with a prior expectation of network structure. This prior expectation can be uninformative, or it may include prior knowledge about the study system. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

      We start from the perspective of a community ecologist wishing to describe an interaction network. This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}. While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not the interaction truly occurred} (Fig.~\ref{conceptual_fig}). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}, leaving some uncertainty about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L_{ij}=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$. It is unlikely that $\chi_{ij}=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij}<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies. Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample extensively in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

@@

        \subsubsection*{Did we observe the interaction?}

          Lastly, measurement errors are a pervasive source of uncertainty about ecological processes. Even if an interaction is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), it may still go undetected~\citep{Jordano2016,Weinstein2017}. We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$. Detection failure could happen for many reasons (see~\citet{Wirta2014}). Some sources of detection error can be minimised with appropriate sampling (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}. The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.

    % \subsection*{Can't we just sample more?}

    To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

    The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij}=1$ but process or detection uncertainty is high). High-quality sampling is undoubtedly a crucial part of constructing an empirical network, but there are limits to the utility of increased sampling (see \emph{Appendix S2}). To compliment high-quality sampling, we can reduce uncertainty by combining the observed data available with prior knowledge about the system. This is straightforward to do using a Bayesian approach, as detailed below.

@@

    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k=0$ cases. We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda_{ij}$ is:

    %     \begin{equation}
    %       \lambda_{MLE}=\frac{k}{n}  .
    %       \label{theta_MLE}
    %     \end{equation}

    % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k=0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L=1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij}=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

@@

    % All of the above methods for estimating the variance of $\lambda_{ij}$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda=0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
